HTW Project

### 2023-10-16 HTW.qmd
fix image issue

---
title: HTW Project
date: last-modified
page-layout: full
bibliography: "Bib/HTW.bib"
code-fold: true
code-tools: true
execute: 
  warning: false
  eval: true
---

@@

# Introduction

@@

Following the procedure used by McDaniel & Busemeyer (2009), we will
assess the ability of both ALM and EXAM to account for the empirical
data when fitting the models to 1) only the training data, and 2) both
training and testing data. Models will be fit directly to the trial by
trial data of each individual participants, both by minimizing the
root-mean squared deviation (RMSE), and by maximizing log likelihood. Because ALM
has been shown to do poorly at accounting for human patterns extrapolation [@deloshExtrapolationSineQua1997], we will also
fit the extended EXAM version of the model, which operates identically to ALM during training, 
but includes a linear extrapolation mechanism for generating novel responses during testing.

\
\
\
\
\
\
\

>>>>

---
title: HTW Project
date: last-modified
page-layout: full
bibliography: "Assets/Bib/HTW.bib"
code-fold: true
code-tools: true
execute: 
  warning: false
  eval: true
---

@@

```
# Introduction

@@

Following the procedure used by McDaniel & Busemeyer (2009), we will
assess the ability of both ALM and EXAM to account for the empirical
data when fitting the models to 1) only the training data, and 2) both
training and testing data. Models will be fit directly to the trial by
trial data of each individual participants, both by minimizing the
root-mean squared deviation (RMSE), and by maximizing log likelihood. Because ALM
has been shown to do poorly at accounting for human patterns extrapolation [@deloshExtrapolationSineQua1997], we will also
fit the extended EXAM version of the model, which operates identically to ALM during training, 
but includes a linear extrapolation mechanism for generating novel responses during testing. 
[@albaretDifferentialEffectsTask1998]
\
\
\
\
\
\
\
